On optimisation in HDR brachytherapy

### 2015-03-04 Paper BMT/article-sample-proceedings.tex
Edited the BMT paper

\title{Insert your title here}
\runningtitle{Short title}
%\subtitle{Insert subtitle if needed}

\author*[1]{First Author}
\author[2]{Second Author}
\author[2]{Third Author} 
\runningauthor{F.~Author et al.}

\affil[1]{\protect\raggedright 
  Institution, address of first, e-mail: author\_one@rmi.ge}
\affil[2]{\protect\raggedright 
  Institution, address of second author and third author, e-mail: author\_two@rmi.ge, author\_three@rmi.ge}

@@

\keywords{Please insert your keywords here, separated by commas.}

@@

\section{Headline 1st level}

Please insert your manuscript here. \textit{Please insert your manuscript here}. Please insert your manuscript here. Please insert your manuscript here. \textbf{Please insert your manuscript here}. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

New paragraph: Please insert your manuscript here in \citep{2,3,4,5}. Please insert your manuscript here in \citep{1}. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

\subsection{Headline 2nd level}
Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

New paragraph: Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here, see Table \ref{tab:Table1}. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

\begin{table}
\caption{Please insert your table caption here.}
\begin{tabular}{llr}
Table head 1 			& Table head 2 			& Table head 3 		\\ \midrule
Table content 1a 	& Table content 2a 	& Table content 3 \\
Table content 1b	& Table content 2b	& 0.1111 					\\
Table content 1c	& Table content 2c 	& 0.3333 					\\
\end{tabular}
\label{tab:Table1}
\end{table}

\subsubsection{Headline 3rd level}
Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

New paragraph: Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.
Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

\begin{itemize}
\item Item 1
\item Item 2
\end{itemize}

New paragraph: Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here (see Figure \ref{img:Figure1}).

New paragraph: Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

%If possible, please provide figures in the grayscale or CMYK color mode rather than the RGB mode%
\begin{figure}
	\includegraphics[width=\columnwidth]{graphics/figure1}
	\caption{Please insert your figure caption here.}
	\label{img:Figure1}
\end{figure}

\paragraph{Headline 4th level}
Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

New paragraph: Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here. Please insert your manuscript here.

In the subsequent discussion we can conveniently set
$$g=g_{0}, \quad a=a_{0}, \quad x=x_{0}+x_{1}2+x_{2}2^{2}+ \cdots +x_{n}2^{n}$$
$0 \leqslant x_{0}+x_{1}2+x_{2}2^{2}+ \cdots +x_{n}2^{n} \leqslant q-2,$
where $x_{i} \in \{0,1 \}$, for $0 \leqslant i \leqslant n$, and then
rewrite the relation (\ref{eq:1}) in the form

\begin{equation}\label{eq:1}
g_{0}^{x_{0}+x_{1}2+x_{2}2^{2}+ \cdots +x_{n}2^{n}}=a_{0} \mbox{ ,}
\end{equation}
Rising both parts of the last equation to the power $(q-1)/2$ and
taking into account that the following relation ...

\begin{enumerate}
\item Item 1
\item Item 2
\end{enumerate}

\begin{acknowledgement}
Please insert acknowledgments of the assistance of colleagues or similar notes of appreciation here.
\end{acknowledgement}

@@

% Books
\bibitem{1}
Eisen HN. Immunology: an introduction to molecular and cellular
principles of the immune response. 5th ed. New York: Harper and
Row 1974.

% Institutional publications:
\bibitem{2}
Institute of Medicine (US). Looking at the future of the Medicaid
program. Washington: The Institute 1999.

% Chapters in books:
\bibitem{3}
Weinsten L, Swartz MN. Pathogenic properties of invading
microorganisms. In: Sodeman WA Jr, Sodeman WA, editors. Pathologic
physiology: mechanisms of disease. Philadelphia: WB Saunders 1974:
457--472.

% Articles in journals with up to 6 authors:
\bibitem{4}
Ge Q, Filip L, Bai A, Nguyen T, Eisen HN, Chen J. Inhibition
of influenza virus production in virus-infected mice by RNA interference.
Proc Natl Acad Sci USA 2004; 101: 8676--8681.

% Articles in journals with more than 6 authors:
\bibitem{5}
You CH, Lee KY, Chey WY, et al. Electrogastrographic study
of patients with unexplained nausea, bloating and vomiting. Gastroenterology 1980; 79: 311--314.

>>>>

\title{On optimisation in HDR brachytherapy}
\runningtitle{On optimisation in HDR brachytherapy}
%\subtitle{Insert subtitle if needed}
\author[1]{Laurin Mordhorst}
\author[2]{Thobias Karthe}
\author[2]{Sebastian Elm}
\author[2]{Dawid Golebiewski} 
\author[2]{Malte Erik Schröder}
\runningauthor{Mordhorst, L.; Karthe, T.; Elm, S.; Golebiewski, D.; Schröder, M. E.}

\affil[1]{\protect\raggedright 
  TUHH,  e-mail: laurin.mordhorst@tuhh.de}
\affil[2]{\protect\raggedright 
  TUHH,  e-mail: thobias.karthe@tuhh.de, sebastian.elm@tuhh.de, dawid.golebiewski@tuhh.de, malte.schroeder@tuhh.de}

@@

\keywords{Optimisation, Treatment planning, Brachytherapy, Genetic Algorithm, Simulated Annealing, Linear Programmin}

@@

\section{Introduction}

The aim of this article is to compare three different approaches in HDR-Brachytherapy treatment planning. The three analysed algorithms are linear programming, simulated annealing and genetic algorithms. The results are evaluated by analysing the conformity and homogenity of the dose-distribution as well as runtime for different parameters.

\section{Genetic Algorithm}
The Genetic Algorithm as introduced in \citep{1} has a lot of paramters which are described in the following.

\subsection{Parameters}

\subsubsection{Weights}
The Fitness-Function used in the Genetic Algorithm is implemented as a sum of squared distances. But every tissue type can be weighted with an individual coefficent. Different weightings for the tissue types should clearly visible in the DVH.

\subsubsection{Probabilities} 
There are two important probabilites within the algorithm. The first one is the crossover rate. It describes how likely it is for two individuals to reproduce. The second one is the mutation rate. It describes, analogous to the crossover rate, the probability for an individual to perform a mutation. \\
Higher probabilties should cause higher fluctuations within the population. This may effect the runtime, because the individuals may change even when a steady state is reached, so the termination criterion is not fullfilled.

\subsubsection{Scaling and Accuracy}
The fitness-function for the given optimisation problem has very high computational complexity. Hence two scaling parameters are introduced to achieve shorter runtimes. The challenge here is to find a compromise between good accuracy for the optimisation and practicable runtimes.\\ The first parameter is called the \textit{treatment range}. It chooses the range around the PTV which shall be evaluated by the algorithm. The second parameter is a simple scaling value which defines that just every  $n^{th}$ voxel is evaluated. Within the treatment range of course.

\subsection{Results}

\subsubsection{Weights}
The results have shown that the best CI and HI is achieved by a weighting composition of bla bla bla. But it should be mentioned, that the weightings should be different for every patient. It seems very unlikely to find a set of weighting coefficents, which achieves equally good results for a broader spectrum of patients.

\subsubsection{Probabilities} 
The results have shown, that some values are better than others.

\subsubsection{Scaling and Accuracy}
The dose distribution of a radioactive seed shows that the dose at a radius of 10 cm is negligible small. So any treatment range higher than 10 cm wouldn't lead to better results anyway. (TODO: which range is acceptable)
\begin{acknowledgement}
Please insert acknowledgments of the assistance of colleagues or similar notes of appreciation here.
\end{acknowledgement}

@@

% Books

\bibitem{1}
Koza, John R. Genetic Programming. 3rd ed. Cambridge: MIT Press 1992.
